Kyoto VR MQP Paper First Draft

### 2019-09-20 paper.tex
add acknowledgments

>>>>

We would like to thank Atticus Sims, CEO and founder of Kyoto VR, for sponsoring
this project and providing help and guidance throughout our time in Japan. His
knowledge of the history of Kinkaku-ji and Kyoto in general has been invaluable
to our experience.

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer.

Finally, a thank you to our advisers: Professors Joshua Cuneo and Ralph Sutter.
Without their expert advice and feedback this project probably could not have
been completed.
